Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-05 Response to reviewers.tex

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment: Response to Reviewers\' comments}

\noindent
Dear Sirs,\\

First, we would like to express our gratitude to you, the editorial team, and the reviewers whose valuable comments on this paper have significantly improved its quality. We have addressed all the comments in the new version of the paper and will list all the changes item-by-item in response to the mentioned comments below. \\

\noindent
Yours sincerely,\\
The authors.

\section{Comments by Reviewer \#1}

\noindent There are some issues needed to be aaddressed further: \\

\noindent (1) Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF ? \\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (2) In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ? For RF, how many trees are set ?\\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (3) As we known, tree-based mehods (e.g.,M5P and RF) themselve embed feature selection procedure. That is, some features are choosen to build trees. It is not fair enough to compare five methods in Table 3. \\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (4) It seems more reasonable to organize and write that paper according to regression viewpoint only.\\

\begin{verbatim}
Our response here
\end{verbatim}

\noindent (5) It is necessary to write that paper more concisely.\\

\begin{verbatim}
Our response here
\end{verbatim}

\section{Comments by Reviewer \#2}

\noindent This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors:\\

\noindent (1) The ANN and ELM (extreme learning machine) should be added into the experiments;\\

\noindent (2) The authors should clarify their main contributions in the introduction parts.\\

\noindent (3) Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part.\\

\noindent (4) Some tables should be transfer to figures because there are too many figures.\\

\noindent (5) Graphical abstract should be added.
This paper is organized well. The authors should revise their work according to above comments.\\

\section{Comments by Reviewer \#3}

\noindent There are several concerns should be considered. \\

\noindent (1) In section introduction, this manuscript should describe the contribution of this work.\\

\noindent (2) In sections 4.1 and 4.2 should be moved to section 2.\\

\noindent (3) In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it.\\

\noindent (4) In Section 5, parameter settings of M5P, kNN and RF also should be shown.

\end{document}

### 2016-08-12 paper.tex
Waiting at the airport
And revising introduction as instructed by #45. Maybe @pacastillo or @fergunet could have a look. I have the impression that it is excessively iterative and that it does not follow a clear line of reasoning, not to mention that it does not hightlight our actual contribution. I will continue with this anyway.

Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution, and storage processes; most of these costs are associated
with the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that there is an unknown
author or a new topic with no track record. Sales forecasts can
only be based on the knowledge obtained from other similar products,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, doing accurate
estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}.

This problem is specially acute for book publishers, who, among other
content providers, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to a lack of supply or in bad marketing for the customers, for instance.

>>>>

Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of its processes of production,
distribution, and storage. Most of these costs are associated
with the number of books actually printed, the so called {\em print run}. But the problem is further
complicated for completely new products, in the sense that they have been written by an unknown
author or deal with a new topic with no track record. In order to make
the print run as close as possible to actual sales, it is essential to
have an estimation of those sales; that is the challenge we are taking
in this paper.

In general, forecasting the sales of cultural products can
only be based on the knowledge obtained from sales of other, similar, ones,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, making accurate
estimations of future sales of the new product is quite difficult, and
extremely important, so that production runs follow predicted sales.  
Indeed, several studies have demonstrated that improving sales
predictions, that is reducing the error in estimated sales, results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}, so not only cost
associated to the book itself are associated, but also the whole
production process.

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers, who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to a lack of supply
or in bad marketing for the customers, for instance.
